### 2017-11-13 linearity-2018/introduction.tex
A few additions.

Suppose $\cat{M}_1$ and $\cat{M}_2$ are two categories with a
bifunctor $\odot_i : \cat{M}_i \times \cat{M}_i \mto \cat{M}_i$, a
distinguished object $I_i \in \mathsf{Obj}(\cat{M}_i)$, and the two
natural isomorphisms $\lambda_A : A \odot I_i \mto A$ and $\rho_A :
I_i \odot A \mto A$.  We call these categories \emph{magmoidal
  categories with a unit}.  Examples of magmoidal categories with a
unit are monoidal categories, symmetric monoidal categories, and
cartesian closed categories.  Benton's LNL models can be generalized
to magmodial categories.  Simply, take an adjunction $\cat{M}_1 : F
\dashv G : \cat{M}_2$ called an \emph{adjoint model} where the
functors $F$ and $G$ preserve the magmoidal structure similarly to
monoidal functors, but without the coherence diagram for the
associator.  Now if we add to $\cat{M}_1$ and $\cat{M}_2$ some
structural rules, for example, by making $\cat{M}_1$ a symmetric
monoidal category and $\cat{M}_2$ a monoidal category, then we obtain
an adjoint model that corresponds to a logic where intuitionistic
linear logic ($\cat{M}_1$) and the Lambek calculus ($\cat{M}_2$) are
mixed similarly to LNL models.  However, this also leads to a new
solution to an existing problem.

>>>>

Our main contributions in this paper are to the Lambek Calculus, but
we make use of a new more general framework that will put this work in
line with planned future work.  Suppose $\cat{M}_1$ and $\cat{M}_2$
are two categories with a bifunctor $\odot_i : \cat{M}_i \times
\cat{M}_i \mto \cat{M}_i$, a distinguished object $I_i \in
\mathsf{Obj}(\cat{M}_i)$, and the two natural isomorphisms $\lambda_A
: A \odot I_i \mto A$ and $\rho_A : I_i \odot A \mto A$.  We call
these categories \emph{magmoidal categories with a unit}.  Examples of
magmoidal categories with a unit are monoidal categories, symmetric
monoidal categories, and cartesian closed categories.  Benton's LNL
models can be generalized to magmodial categories.  Simply, take an
adjunction $\cat{M}_1 : F \dashv G : \cat{M}_2$ called an
\emph{adjoint model} where the functors $F$ and $G$ preserve the
magmoidal structure similarly to monoidal functors, but without the
coherence diagram for the associator.  Now if we add to $\cat{M}_1$
and $\cat{M}_2$ some structural rules, for example, by making
$\cat{M}_1$ a symmetric monoidal category and $\cat{M}_2$ a monoidal
category, then we obtain an adjoint model that corresponds to a logic
where intuitionistic linear logic ($\cat{M}_1$) and the Lambek
calculus ($\cat{M}_2$) are mixed similarly to LNL models.  However,
this also leads to a new solution to an existing problem.
